Prefetching SPARQL query cacher

### 2016-06-05 dissertation/cache-proxy.tex
improve on graph names

The system is in the convergence of the directions described in this
dissertation: It should relieve the remote endpoint of some of the
burden to evaluate the query and it should add to the robustness of the
open Web SPARQL infrastructure. It uses hypermedia to answer individual
triple patterns, based on Triple Pattern Fragments (TPF) \cite{ldf1}. The
system can only answer triple patterns, but other than that, supports
SPARQL 1.1 in its entirety. This was made possible to develop quickly
by the efforts put into the query planning in the Attean framework
described in Section~\ref{sec:conpush}. Caching based on RFC7234
\cite{rfc7234} was shown to be of possible use in the survey I
conducted. Finally, it was planned to be evaluated using
Design of Experiments.

>>>>

The system is in the convergence of the directions described in this
dissertation: It should relieve the remote endpoint of some of the
burden to evaluate the query and it should add to the robustness of
the open Web SPARQL infrastructure. It uses hypermedia to answer
individual triple patterns, based on Triple Pattern Fragments (TPF)
\cite{ldf1}. The system does not support named graphs (i.e. only
triple stores), but other than that, supports SPARQL 1.1 in its
entirety. This was made possible to develop quickly by the efforts put
into the query planning in the Attean framework described in
Section~\ref{sec:conpush}. Caching based on RFC7234 \cite{rfc7234} was
shown to be of possible use in the survey I conducted. Finally, it was
planned to be evaluated using Design of Experiments.
